Matching Bullets

### 2015-12-04 imaging-paper.Rnw
slowsly adjusting the figures to the new matching routine

\begin{figure}
\centering
    \begin{subfigure}[t]{\linewidth}
\caption{Loess smooth at $x = 100$ (span is 0.03).\label{fig:smooth}}{%
<<smooth, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
qplot(data=lofX, y, resid, colour=bullet, size=I(0.75), geom="line", group=bullet) +
  geom_line(aes(y=l30), colour="grey30", size=0.5) +
  facet_grid(bullet~.) +
  scale_colour_brewer("", palette="Set1") +
  theme_bw() +
  theme(legend.position="none")
@
    }
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{Values above/below a threshold level are defined as peaks and grooves. \label{fig:smoothcutb}}{%
<<smoothcut, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=4, out.width='\\textwidth', warning=FALSE>>=
qplot(data=lofX, x=y, y=l30, colour=type, geom="line", 
      group=bullet, size = I(0.75)) + 
  facet_grid(bullet~.) +
  ylab("Individual characteristics") + 
#  geom_point(aes(y=r05)) +
  geom_rect(xmin = 200, xmax = 2260, ymin = -.75, ymax = 0.75, colour=NA, fill=alpha("grey90", alpha =0.5)) +
  scale_colour_brewer(palette="Set2", na.value = NA) +
  theme_bw() +
  theme(legend.position="bottom")
@
    }
\end{subfigure}    
\begin{subfigure}[t]{\linewidth}
    \caption{Grey backgrounds identify a line on one of the bullets. Overlaps of the same color indicate matching striation marks.
    Matching striations are marked by an `o', mismatches are marked by an `x'.   \label{fig:smoothcutd}}{%
<<smoothmatch, echo=FALSE, dependson='twolands100match', fig.width=7, fig.height=2.75, out.width='\\textwidth'>>=
ggplot() +
  geom_rect(aes(xmin = miny, xmax = maxy), ymin = 0.25, ymax=2.75, fill="grey80", data = subset(lines, lineid != 0)) +
  geom_tile(data=lofX, aes(x=y, y=bullet, fill=type)) + 
  scale_y_discrete(expand = c(0.2,0)) +
  scale_fill_brewer(palette="Set2") + 
  theme_bw() +
  ylab("") +
  theme(legend.position="bottom") +
  geom_text(aes(x = meany), y= .4, label= "x", data = subset(lines, !match & lineid !=0)) +
  geom_text(aes(x = meany), y= .4, label= "o", data = subset(lines, match & lineid !=0))
@
    }
\end{subfigure}
\caption{\label{fig:match} Matching striation marks: smooth (a), cut (b), and match (c).}
\end{figure}

@@

\subsection{Varying threshold}

In order to address the subjectivity involved in choosing a threshold level, we investigate this parameter more closely. Figure~\ref{fig:thresholds} shows the relationship between threshold and the maximal number of consecutive matching striae. For thresholds between 0.7 and 0.9 the number of CMS peaks at fifteen. On average, there are 6.6 CMS across the range of thresholds. In the autmatic matching routine, several thresholds are considered and the threshold resulting in the higest number of consecutive atching striae is chosen (and reported).
\begin{figure}
<<thresholds, echo=FALSE, fig.width = 7, fig.height = 3, out.width = '0.49\\textwidth'>>=
thresholds <- seq(0.3, 1.5, by = 0.025)
CMS <- thresholds %>% lapply(function(threshold) {
 lines <- striation_identify(lofX, threshold = threshold)
 cms <- CMS(lines$match)
 data.frame(threshold=threshold, maxCMS = as.numeric(rev(names(cms)))[1])
}) %>% bind_rows()

qplot(threshold, maxCMS, data=CMS) + theme_bw() +
  ylab("Number of maximal CMS") +
  ylim(c(0,15))
@
\caption{\label{fig:thresholds}Varying the threshold levels results in different number of consecutive matching striae between the two bullets. By default, the threshold with the highest CMS is chosen automatically.}
\end{figure}

@@

\hh{Things we discussed}
\begin{enumerate}
\item adding more non-matches into the mix is going to make things more realistic. 
\end{enumerate}
\bibliographystyle{abbrv}
%%use following if all content of bibtex file should be shown
%\nocite{*}
\bibliography{references}

>>>>

\begin{figure}
\centering
    \begin{subfigure}[t]{\linewidth}
\caption{Loess smooth at $x = 100$ (span is 0.03).\label{fig:smooth}}{%
<<smooth, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
qplot(data=lofX, y, resid, colour=bullet, size=I(0.75), geom="line", group=bullet) +
  geom_line(aes(y=l30), colour="grey30", size=0.5) +
  facet_grid(bullet~.) +
  scale_colour_brewer("", palette="Set1") +
  theme_bw() +
  theme(legend.position="none")
@
    }
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{Using a rolling median peaks and grooves are identified for each crosscut. \label{fig:smoothcutb}}{%
<<smoothcut, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=4, out.width='\\textwidth', warning=FALSE>>=
  lof <- processBullets(paths = images[c(5,7)], x = 100)
  lof <- bulletSmooth(lof)
  bAlign = bulletAlign(lof)
  lofX <- bAlign$bullet

  b12 <- unique(lof$bullet)
  peaks1 <- get_peaks(subset(lofX, bullet==b12[1]), smoothfactor = 30)
  peaks2 <- get_peaks(subset(lofX, bullet == b12[2]), smoothfactor = 30)
  p1 <- peaks1$plot + xlab("y") + ylab("smoothed crosscut") + ggtitle(b12[1])
  p2 <- peaks2$plot + xlab("y") + ylab("smoothed crosscut") + ggtitle(b12[2])
grid.arrange(p1, p2, ncol=1)
@
}
\end{subfigure}    
\begin{subfigure}[t]{\linewidth}
    \caption{Rectangles in the back identify a line on one of the bullets.  Matching striation marks are indicated by color filled rectangles and arked by an `o'. Mismatches are filled in grey and  marked by an `x'.   \label{fig:smoothcutd}}{%
<<smoothmatch, echo=FALSE, dependson='twolands100match', fig.width=7, fig.height=2.75, out.width='\\textwidth'>>=
peaks1$lines$bullet <- b12[1]
peaks2$lines$bullet <- b12[2]

lines <- striation_identifyXXX(peaks1$lines, peaks2$lines)

ggplot() + 
  geom_rect(aes(xmin = xmin, xmax = xmax, fill=factor(type)), ymin = -6, ymax=6,  data = lines, alpha=0.2) +
  theme(legend.position="bottom") +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(lines, match)) +
  ylim(c(-6,6)) + theme_bw() +
  geom_line(data=lofX, aes(x=y, y=l30, group=bullet, colour=bullet)) +
  scale_colour_brewer("", palette="Set1") +
  scale_fill_brewer("", palette="Set2", na.value=alpha("grey60", 0.5)) +
  theme(legend.position="none") +
  ylab(expression("Crosscut values in",mu,m)) +
  xlab("y")

# ggplot() +
#   geom_rect(aes(xmin = miny, xmax = maxy), ymin = 0.25, ymax=2.75, fill="grey80", data = subset(lines, lineid != 0)) +
#   geom_tile(data=lofX, aes(x=y, y=bullet, fill=type)) + 
#   scale_y_discrete(expand = c(0.2,0)) +
#   scale_fill_brewer(palette="Set2") + 
#   theme_bw() +
#   ylab("") +
#   theme(legend.position="bottom") +
#   geom_text(aes(x = meany), y= .4, label= "x", data = subset(lines, !match & lineid !=0)) +
#   geom_text(aes(x = meany), y= .4, label= "o", data = subset(lines, match & lineid !=0))
@
    }
\end{subfigure}
\caption{\label{fig:match} Matching striation marks: smooth (a), identify peaks and valley (b), and match peaks and valleys between crosscuts (c).}
\end{figure}

@@

%' \subsection{Varying threshold}
%' 
%' In order to address the subjectivity involved in choosing a threshold level, we investigate this parameter more closely. Figure~\ref{fig:thresholds} shows the relationship between threshold and the maximal number of consecutive matching striae. For thresholds between 0.7 and 0.9 the number of CMS peaks at fifteen. On average, there are 6.6 CMS across the range of thresholds. In the autmatic matching routine, several thresholds are considered and the threshold resulting in the higest number of consecutive atching striae is chosen (and reported).
%' \begin{figure}
%' <<thresholds, echo=FALSE, fig.width = 7, fig.height = 3, out.width = '0.49\\textwidth'>>=
%' thresholds <- seq(0.3, 1.5, by = 0.025)
%' CMS <- thresholds %>% lapply(function(threshold) {
%'  lines <- striation_identify(lofX, threshold = threshold)
%'  cms <- CMS(lines$match)
%'  data.frame(threshold=threshold, maxCMS = as.numeric(rev(names(cms)))[1])
%' }) %>% bind_rows()
%' 
%' qplot(threshold, maxCMS, data=CMS) + theme_bw() +
%'   ylab("Number of maximal CMS") +
%'   ylim(c(0,15))
%' @
%' \caption{\label{fig:thresholds}Varying the threshold levels results in different number of consecutive matching striae between the two bullets. By default, the threshold with the highest CMS is chosen automatically.}
%' \end{figure}

@@

\hh{Things we discussed}
\begin{enumerate}
\item the Hamby study only includes 35 bullets - this is not a particularly realistic scenario for automatic matching. Adding more non-matches into the mix is going to make things more realistic. 
\end{enumerate}
\bibliographystyle{abbrv}
%%use following if all content of bibtex file should be shown
%\nocite{*}
\bibliography{references}
